%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume_new} % Use the custom resume.cls style
\usepackage{verbatim}
\usepackage[left=0.7in, top=0.5in, right=0.7in, bottom=0.5in]{geometry} % Document margins
\usepackage[cmex10]{amsmath}

\name{Yongming Ding} % Your name
\address{ (+86) 180-3705-3593 \ \\ dingyongming1995@gmail.com \ \\ Homepage: http://dmt.moe/}
%\address{Github: https://github.com/dreamtalen/} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
 % Your phone number and email


\begin{document}
%---------------------------------------------------------------------------------------- 

\begin{rSection}{education}
\textbf{Shanghai Jiao Tong University (SJTU), Shanghai}
\\Master of Science in Electronic Science and Technology \hfill \emph{Sep. 2016 -- Present}
\\\bm{$\diamond$} Major GPA: 3.86/4.00 \qquad Ranking: 8/116 \qquad $\diamond$ Overall GPA: 3.72/4.00
%\\\bm{$\diamond$} Major GPA: 3.86/4.00 \qquad \qquad \qquad \qquad \qquad \, \ \ $\diamond$ Overall GPA: 3.72/4.00
\\\bm{$\diamond$} $1^{st}$ Prize in 12th China Graduate Electronics Design Contest (Ranked $2^{nd}$ in more than 100 teams in the final)
\\Bachelor of Science in Microelectronics \hfill \emph{Sep. 2012 -- Jun. 2016}
\\\bm{$\diamond$} Major GPA: 87.70/100 \qquad Ranking: 8/50 \qquad \ $\diamond$ Overall GPA: 86.27/100
\\\bm{$\diamond$} Major GPA: 89.30/100(upper division) \qquad \qquad$\diamond$ Overall GPA: 89.13/100(upper division)
\\\bm{$\diamond$} Received a waiver for the National College Entrance Exam to enter SJTU, as $1^{st}$ Prize in National Olympiad in Physics (Henan Province, top 0.01$\%$)
\end{rSection}

\begin{rSection}{Professional Experience}
\textbf{Shanghai Jiao Tong University, Shanghai} \hfill \emph{Feb. 2017 -- Jun. 2017}
\\\emph{Teaching Assistant} \hfill \emph {Course Design for Digital Integrated Circuit Design (MR322) }\\
\begin{rSubsection}{Ctrip Computer Technology Co.,Ltd., Shanghai}{July 2015 -- Dec. 2015}{Software Engineer Intern}{Application Management Group, Ctrip Infrastructure Service}
\item Developed and improved software tools to enhance site reliability and boost the efficiency of developing  products.
\item Constructed \textbf{``Alert-Subscribe'', an alert event subscription system}. Completed the back-end job including obtaining alert events periodically, classifying alert events with RegEx and sending notification to subscribers.
\item Designed and implemented \textbf{``Prometheus'', a web service cluster consumers display platform}, to show the dependency relationships between web service clusters, using Django as a back-end framework, using Bootstrap as the front-end framework, and using MySQL and Redis database to store tasks scheduling queue.
\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Publications}
\textbf{Yongming Ding}, Wei Jin, Guanghui He, Weifeng He. ``Short Path Padding with Multiple-Vt cells for Wide-Pulsed-Latch Based Circuits at Ultra-Low Voltage.'' \emph{IEEE International Conference on ASIC}  (2017). Accepted.
\end{rSection}

\begin{rSection}{RESEARCHES AND PROJECTS}
\begin{rSubsection}{Short Path Padding Technique Design}{July 2016 -- present}{}{}
\item Designed and implemented a short path padding software system employing integer linear programming method, which supports up to a wide pulse of 1/3 cycle time in pulsed-latch pipelines.
\item Proposed step-by-step based and path group based schemes to reduce 80.9\% runtime of the baseline padding algorithm and used multiple-Vt buffer cells to reduce additional hardware cost by 52.3\%, on average. 
\end{rSubsection}

\begin{rSubsection}{Image Super-Resolution Using Convolutional Neural Network(CNN)}{July 2017}{}{}
\item Applied deep learning techniques to sharpen or improve the quality of a low-resolution image input by outputting a super-resolved high-resolution image. Proposed a 7-layers CNN which got lower loss value and reduced 10\% training time, compared with ``waifu2x'', an open source image super-resolution software.
\end{rSubsection}

\begin{rSubsection}{``Eye of Providence'', an Intelligent Monitoring System}{May 2017}{}{}
\item Led a group of 4 teammates to build an intelligent classroom monitoring system using face recognition, facial expression detection and speech identification techniques during ``Hackathon SJTU 2017''.
\end{rSubsection}

\begin{rSubsection}{Three-dimensional Integrated Circuit(3D-IC) Partitioning Technique Design}{Jan. 2016 -- Jun. 2016}{}{}
\item Excellent graduate thesis in Department of Micro-Nano Electronics, Shanghai Jiao Tong University.
\item Designed a 3D-IC partitioning algorithm for motion estimation(ME) module of HEVC, including an initial partition algorithm based on breadth first search and an iterative optimization algorithm. Achieved an optimum partition for the ME module, which reduced 42.9\% of the cut edges while the area utilization rate reached 95.5\%.
\end{rSubsection}

\begin{comment}
\begin{rSubsection}{``Yorozuya'', a Campus Labor and Information Exchange Platform}{Nov. 2014}{}{}
\item Developed a web application for campus users to exchange labor and information in ``Hackathon SJTU 2014'' with a teammate. Users can release tasks on this app while the others can choose and finish jobs for reward.
\end{rSubsection}
\end{comment}
\end{rSection}

\begin{rSection}{HONORS, AWARDS and certificates}
Tang Youshu Scholarship, Shanghai Jiaotong University (4 recipients out of 116 students) \hfill \emph{2017}
\\$3^{rd}$ Prize in National Post-Graduate Mathematic Contest in Modeling \hfill \emph{2017}
\\First-class Academic Graduate Student Scholarship, Shanghai Jiao Tong University  \hfill \emph{2016}
\\Senior skill level computer programmer (JAVA, ARM), Occupational qualification certificate, China \hfill \emph{2015 \& 2016}
\\The Best Creative Award, Shanghai Jiaotong University Hackathon \hfill \emph{2015}
\\Scholarship of Academic Excellence, Shanghai Jiao Tong University \hfill \emph{2014 \& 2013}
\\Outstanding Student, Shanghai Jiao Tong University \hfill \emph{2014 \& 2013}
\\$2^{nd}$ Prize in Shanghai Region, National College Student Physics Competition \hfill \emph{2013}
\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
