%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume_ucla} % Use the custom resume.cls style
\usepackage{verbatim}
\usepackage[left=0.6in, top=0.6in, right=0.6in, bottom=0.4in]{geometry} % Document margins
\usepackage[cmex10]{amsmath}

\name{Yongming Ding} % Your name
\address{ (+1) 412-209-5646 \ \\ yongmind@andrew.cmu.edu \ \\ www.linkedin.com/in/yongming-ding/}
%\address{Github: https://github.com/dreamtalen/} % Your address
\address{5030 Centre Ave, Room 255 \\ Pittsburgh, PA 15213} % Your secondary addess (optional)
 % Your phone number and email


\begin{document}
%---------------------------------------------------------------------------------------- 

\begin{rSection}{education}
\begin{rSubsection}{Carnegie Mellon University - Information Networking Institute}{Pittsburgh, PA}{Master's of Science in  Information Technology (Mobility)}{Aug. 2018 -- May. 2020 (expected)}
\item GPA: N/A \qquad Scholarship: INI Scholarship
\item Coursework(*current): Introduction to Computer System (A), Web Application Development*, Storage Systems*
\end{rSubsection}
\begin{rSubsection}{Shanghai Jiao Tong University}{Shanghai, China}{Master of Science in Electronic Science and Technology}{Sep. 2016 -- Mar. 2019 (expected)}
\item Major GPA: 3.86/4.00 \qquad Ranking: 8/116 \qquad $\diamond$ Overall GPA: 3.72/4.00
\item $1^{st}$ Prize in 12th China Graduate Electronics Design Contest (Ranked $2^{nd}$ in more than 100 teams in the final)
\item 2017 Tang Youshu Scholarship, Shanghai Jiaotong University (4 recipients out of 116 students)

\end{rSubsection}
\begin{rSubsection}{Shanghai Jiao Tong University}{Shanghai, China}{Bachelor of Science in Microelectronics}{Sep. 2012 -- Jun. 2016}
\item Major GPA: 3.77/100 \qquad Ranking: 8/50 \qquad \ $\diamond$ Overall GPA: 3.57/100
\item 2013 \& 2014 Scholarship of Academic Excellence (Top 30\%), Shanghai Jiao Tong University
\item 2013 \& 2014 Outstanding Student, Shanghai Jiao Tong University 
\item $2^{nd}$ Prize in Shanghai Region, 2013 National College Student Physics Competition
\end{rSubsection}

\end{rSection}

\begin{rSection}{Skills}
\begin{tabular}{ll}
\textbf{Technical \quad} & Python, C/C++, Django, Bootstrap, HTML/CSS, SQL, Javascript, Vue\\
\textbf{Certificates} & Senior skill level computer programmer (JAVA \& ARM), China occupational qualification certificates\\ 
\end{tabular}
\end{rSection}



\begin{rSection}{Professional Experience}

\begin{rSubsection}{Tencent Technology Co., Ltd.}{Shanghai, China}{Software Engineering Intern}{Apr. 2018 -- June 2018}
\item Participated in developing the lung cancer intelligent screening system, which achieved 95\% detection rate. 
\item Responsibilities include screening platform full-stack web development using Django, Vue, and MySQL, debugging, and deployment with Nginx at Fudan University Shanghai Cancer Center. 
\end{rSubsection}

\begin{rSubsection}{Ctrip Computer Technology Co., Ltd.}{Shanghai, China}{Software Engineering Intern}{July 2015 -- Dec. 2015}
\item Constructed ``Alert-Subscribe'', an alert event subscription system helping operation engineers fix alert events. 
\\ Completed the back-end job including obtaining alert events, classifying with RegEx and sending notifications.
\item Built ``Prometheus'', a web service cluster consumers display platform to show the dependency relationships between clusters. Implemented it independently using Django, Bootstrap, MySQL and Redis.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------

\begin{rSection}{Research Experience \& Projects}
\begin{rSubsection}{C Dynamic Storage Allocator @ CMU ICS course Malloc lab}{July 2018}{}{}
\item Implemented a general purpose dynamic storage allocator for C programs using segregated free list with FIFO strategy. Built own version of the \emph{malloc}, \emph{free}, \emph{realloc}, and \emph{calloc} C functions. 
\item By eliminating footers in allocated blocks, decreasing the minimum block size, and setting up special regions of memory for small, fixed-size blocks, achieved a high throughout 16838 Kpos/sec with 71.4\% memory utilization.
\end{rSubsection}

\begin{rSubsection}{``Eye of Providence'', an Intelligent Monitoring System}{May 2017}{}{}
\item Led a group of 4 teammates to build an intelligent classroom monitoring system using face recognition, facial expression detection and speech identification techniques during ``Hackathon SJTU 2017''.
\end{rSubsection}

\begin{rSubsection}{Short Path Padding Technique Design}{July 2016 -- Nov. 2017}{}{}
\item Designed and implemented a short path padding software employing integer linear programming method, which supports up to a wide pulse of 1/3 cycle time in pulsed-latch pipelines. Proposed step-by-step based and path group based schemes to reduce 80.9\% runtime of the algorithm and used multiple-Vt cells to reduce 52.3\% hardware cost.
\item \textbf{Publication}: Yongming Ding, Wei Jin, Guanghui He, Weifeng He.  ``Short Path Padding with Multiple-Vt cells for Wide-Pulsed-Latch Based Circuits at Ultra-Low Voltage.'' \emph{IEEE International Conference on ASIC}  (2017).
\end{rSubsection}

\end{rSection}



%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
